---
title: "Linear Regression in R"
credits: Tanush Arora (student no: 1010411270)
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
```

In this tutorial, we'll learn how to fit a linear regression model using R. We'll work with the built-in `mtcars` dataset and interpret the model results.

### Fit a model below (Exercise 1)
```{r fit-model, exercise=TRUE}
# Fit a linear model using lm()
# Predict mpg based on wt
# Hint: use lm(y ~ x, data = ...)

lm(mpg ~ wt, data = mtcars)

```


---

### **Visualize Results (Exercise 2)**

### Plotting the model
```{r plot-model, exercise=TRUE}
# Use plot() or ggplot2 to visualize the relationship
# Add a regression line

# Hint: plot(mtcars$wt, mtcars$mpg), then add abline(model)

model <- lm(mpg ~ wt, data = mtcars)
plot(mtcars$wt, mtcars$mpg)
abline(model, col = "red")

```


---

### ðŸž **4. Debugging Task (Exercise 3)**

### Fix the broken model code
```{r debug-model, exercise=TRUE}
# This code is broken. Fix the error!
lm(mpg - wt, mtcarz)

# Hint: Check the formula syntax and dataset name
lm(mpg ~ wt, data = mtcars)

```
Great work! We've fit, visualized, and debugged a linear regression model. Thinking about how R communicates errors is a key part of testing code.
